Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-01 R0V0.tex
Merge Ian's change in the control-contraction metric section

\subsection{Background}\label{sec:background}

@@

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control-contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}. Given a control-contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x,u)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.

@@

\begin{theorem}\label{prop:CCM Existence}
	If there exists a control-contraction metric for system \eqref{eq:general system}, then there exists a differential feedback law for system~\eqref{eq:general system:differential} rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop. Moreover, a stabilizing feedback law for system~\eqref{eq:general system} is obtained by integrating the differential feedback law for system~\eqref{eq:general system:differential} along geodesics.
\end{theorem}

>>>>

\subsection{Control Contraction Metrics}\label{sec:background}

@@

\begin{definition}[{\cite{Manchester2014a}}]\label{def:}
	A metric for system \eqref{eq:general system} is said to be a \emph{control contraction metric for system \eqref{eq:general system}} if there exists a constant value $\lambda>0$ such that the condition
	\begin{subequations}\label{eq:Arstein-Sontag}
		\begin{equation}\label{eq:}
			\delta_x\neq0,\quad\delta_x^\top M(x)B(x)=0
		\end{equation}
		implies that the inequality
		\begin{equation}\label{eq:Artstein-Sontag:inequality}
			\delta_x^\top(\dot{M}+A^\top M+MA)\delta_x<\ -2\lambda \delta_x^\top M\delta_x
		\end{equation}
		holds, where $\dot{M}:=\partial_{f+Bu}M$.
	\end{subequations}
\end{definition}
\mypara The set of equations \eqref{eq:Arstein-Sontag} is an adaptation of Artstein-Sontag's condition to the differential system~\eqref{eq:general system:differential}. Given a control contraction metric for system \eqref{eq:general system}, Finsler's lemma (cf. \cite[Lemma 11.1]{CalafioreGhaoui2014}) provides a stabilizing feedback law of the form $\delta_u=K(x,u)\delta_x$ for system \eqref{eq:general system:differential}, defined for every $(x,\delta_x,u)\in\mathbb{R}^n\times\mathbb{R}^n\times\mathbb{R}^m$, where $K:\mathbb{R}^n\times\mathbb{R}^m\to\mathbb{R}^{n\times m}$.

@@

\begin{theorem}\label{prop:CCM Existence}
	If there exists a control contraction metric for system \eqref{eq:general system}, then there exists a differential feedback law for system~\eqref{eq:general system:differential} rendering the equilibrium of the origin globally exponentially stable for system~\eqref{eq:general system:differential} in closed loop. Moreover, a stabilizing feedback law for system~\eqref{eq:general system} is obtained by integrating the differential feedback law for system~\eqref{eq:general system:differential} along geodesics.
\end{theorem}
